\documentclass{informs3}

\usepackage{pst-all}
\usepackage{xspace}
%\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose}
\usepackage{array}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{setspace}
\RequirePackage{natbib}
 \bibpunct[, ]{(}{)}{,}{a}{}{,}%
 \def\bibfont{\small}%
 \def\bibsep{\smallskipamount}%
 \def\bibhang{24pt}%
 \def\newblock{\ }%
 \def\BIBand{and}%
%\doublespacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\makeatother


%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%


\RUNTITLE{Wikipedia Literature Review}
\TITLE{What we know about Wikipedia. A review of the literature analyzing
the project(s).}

\ARTICLEAUTHORS{%
	% Enter all authors
    \AUTHOR{Nicolas Jullien}
	\AFF{IMT Atlantique-UBL, LEGO-M@rsouin, \EMAIL{Nicolas.Jullien@imt-atlantique.fr}
} 
}
\maketitle
\ABSTRACT{
This article proposes a review of the literature analyzing Wikipedia
as a collective system for producing knowledge. It is not a review of all the articles written on Wikipedia, but, more modestly, a review of the existing literature on how Wikipedia
works, based on the framework proposed by Elionor Ostrom and Charlotte Hess to analyze the knowledge commons.
It is and opensource, collaborative works, protected by the license presented in the license.txt file.
}


% Text of your paper here

\section{Introduction}\label{sec:introduction}
\input{01-introduction.tex}

\section{Structure of the Analysis and of the Document}\label{sec:related}
\input{02-aimorganizationdoc.tex}

\section{Inputs}\label{sec:Inputs}
\input{03-input.tex}
\subsection{Environment, Rules in Use}\label{subsec:EnvironmentRules}
\input{03.1-environment-rules.tex}
\subsection{Why do they participate?}\label{subsec:Why-do-they-participate}
\input{03.2-participation.tex}

\section{The process(es), or the patterns of interaction.}\label{sec:Process,-or-the}
\input{04-process.tex}

\section{Conclusion}\label{sec:conclusion}
\input{06-conclusion.tex}
\subsection{The contributors, their activity and roles (what they do).}\label{subsec:The-contributors,-activity}
\input{041-contributorsactivity.tex}

\subsection{Pieces of knowledge, articles, and global structure.}\label{subsec:The-pieces-of-knowledge}
\input{042-piecesofknowledge.tex}

\subsubsection{Structure of the project.}
\input{0421-structureproject.tex}
\subsubsection{Structure of articles edition.}
\input{0422-structurearticle.tex}

\subsection{The organization, structure, and governance of the project.}
\input{043-organizationgovernance.tex}

\subsubsection{People, team and articles.}
\input{0431-peopleteamarticles.tex}
\subsubsection{The life of an article: creation and deletion, redaction, and promotion.}
\input{0432-lifeofanarticle.tex}

\subsubsection{Management and leadership.}
\input{0433-managementleadership.tex}

\subsubsection{Organization, process, a conclusion.}
\input{0434-organizationprocessconclusion.tex}


\section{Evaluation, points of view.}
\label{sec:Evaluation}
\input{05-evaluation.tex}

\subsection{Process Quality and Efficiency.}
\label{subsec:processquality}
\input{051-processquality.tex}

\subsection{Users' experience.}
\label{subsec:usersexperience}
\input{052-usersexperience.tex}

\subsubsection{Developers' experience.}
\input{0521-developerssexperience.tex}

\subsubsection{Readers' experience.}
\input{0522-readerssexperience.tex}

\subsection{Product quality.}
\label{subsec:productquality}
\input{053-productquality.tex}

\subsubsection{Global coverage.}
\input{0531-globalcoverage.tex}

\subsubsection{Articles quality.}
\input{0532-articlesquality.tex}

\subsubsection{Conclusion.}
\input{054-conclusionquality.tex}


% Acknowledgments here
\section*{ACKNOWLEDGMENT}%

\bibliographystyle{inform}
\bibliography{2012andbefore.bib,2013.bib,2014.bib}
\end{document}


